	\begin{titlepage}
		\begin{tikzpicture}[remember picture,overlay,inner sep=0,outer sep=0]
		\draw[blue!70!black,line width=4pt] ([xshift=-1.5cm,yshift=-2cm]current page.north east) coordinate (A)--([xshift=1.5cm,yshift=-2cm]current page.north west) coordinate(B)--([xshift=1.5cm,yshift=2cm]current page.south west) coordinate (C)--([xshift=-1.5cm,yshift=2cm]current page.south east) coordinate(D)--cycle;
		
		\draw ([yshift=0.5cm,xshift=-0.5cm]A)-- ([yshift=0.5cm,xshift=0.5cm]B)--
		([yshift=-0.5cm,xshift=0.5cm]B) --([yshift=-0.5cm,xshift=-0.5cm]B)--([yshift=0.5cm,xshift=-0.5cm]C)--([yshift=0.5cm,xshift=0.5cm]C)--([yshift=-0.5cm,xshift=0.5cm]C)-- ([yshift=-0.5cm,xshift=-0.5cm]D)--([yshift=0.5cm,xshift=-0.5cm]D)--([yshift=0.5cm,xshift=0.5cm]D)--([yshift=-0.5cm,xshift=0.5cm]A)--([yshift=-0.5cm,xshift=-0.5cm]A)--([yshift=0.5cm,xshift=-0.5cm]A);
		
		
		\draw ([yshift=-0.3cm,xshift=0.3cm]A)-- ([yshift=-0.3cm,xshift=-0.3cm]B)--
		([yshift=0.3cm,xshift=-0.3cm]B) --([yshift=0.3cm,xshift=0.3cm]B)--([yshift=-0.3cm,xshift=0.3cm]C)--([yshift=-0.3cm,xshift=-0.3cm]C)--([yshift=0.3cm,xshift=-0.3cm]C)-- ([yshift=0.3cm,xshift=0.3cm]D)--([yshift=-0.3cm,xshift=0.3cm]D)--([yshift=-0.3cm,xshift=-0.3cm]D)--([yshift=0.3cm,xshift=-0.3cm]A)--([yshift=0.3cm,xshift=0.3cm]A)--([yshift=-0.3cm,xshift=0.3cm]A);
		
		\end{tikzpicture}
		\centering
		{\scshape\Large Project Report \linebreak\linebreak On}
		\vs
		{\scshape\Huge \projectname \par}
		\vspace{0.6cm}
		{\large\em towards partial fulfillment of the requirement  \linebreak \linebreak for the award of degree of}
		\vs
		\textbf{\Large \degree}
		\vs
		{\large\em submitted by}
		\vs
		\textbf{\large \me \linebreak \id}				
		\vs
		{\large\em under the supervision of}
		\vs
		\textbf{\large \sir}				
		\vs[1]
		ACADEMIC SESSION 2017 – 2020
		\vs
		\textbf{\large \dept}
		\vs[1.5]
		\logo
		\vs[1.5]
		{\scshape\LARGE \college}
		\vs
		{\scshape\large An Autonoumous College Of University Of Lucknow}
		(NAAC 'A' Grade Credited)		
		\vs
		2 - Rana Pratap Marg, Lucknow, Uttar Pradesh, India.
	\end{titlepage}
	\pagebreak
	\begin{center}
		\logo
		\vs[1.5]
		{\scshape\LARGE \college}
		\vs
		2 - Rana Pratap Marg, Lucknow, Uttar Pradesh, India.
		\vs[1]	
		\textbf{\LARGE Certificate}
		\vs[1]
		{\em \large this is to certify that project report entitled}
		\vs
		{\scshape\Huge \projectname}
		\vs
		{\em \large being submitted by}
		\vs
		\textbf{\large \me \linebreak \id}
		\par
		\vspace{0.6cm}
		{\large\em towards partial fulfillment of the requirement  \linebreak for the award of degree of}			
		\vs
		\textbf{\Large \degree}
		\vs
		{\large In the Academic Session 2017 - 2020}
		\vs
		is a record of students own work
		\linebreak
		and to the best of my knowledge the work reported here in does not form a part of
		\linebreak
		any other thesis or work on the basis of which degree or award was conferred on
		\linebreak
		an earlier occasion to this or any other candidate.

	\end{center}
	\vfill
	\begin{flushright}
		{\scshape\large \hod}
		\linebreak
		Head Of Department	
	\end{flushright}
	\pagebreak
	
	{\centering \scshape\LARGE CANDIDATE DECLARATION \par}
	\vs[1]
	I, hereby certify that the work which is being presented in the project work entitled \textbf{\em \projectname}
	is the fulfillment of the requirement for award of the \textbf{\degree}
	submitted in the \textbf{ \dept\space of \college}. 
	\vs[1]
	This is an authentic record of my work during 5 months period under supervision of \textbf{\sir}. 

	\vs[1]
	The matter presented in the project work has {\em not} been submitted by me for the award of any other
	Degree/Diploma of this or any other University.

	\vs[2]
	\textbf{Date:\space\space\space/\space\space\space/ 2020}		
	\vs
	\textbf{Place: Lucknow, Uttar Pradesh, India.}
	\hfill
	(Signature Of Candidate)
	\pagebreak
	
	{\centering\scshape\LARGE Acknowledgement \par}
	\vs[1]
		
	The satisfaction and euphoria that accompany the development of any task would be incomplete
	without the \textbf{mention of the people} who make it possible, whose constant guidance and
	encouragement crowned our efforts with success.
	\vs
	We, the developers feel indebted to a lot of people who during the course of our project not only held
	us in good stead but also provided us with invaluable services both personal and professional.
	\vs
	At this juncture, when we, at the successful completion of our project are presenting our report it
	would be unfair not to acknowledge the various acts of kindness done to us by our teachers. They
	were always present on our every beck and call to help us out of every hurdle and obstacle that we
	faced.
	\vs
	Our first vote of thanks goes to our \textbf{Parents}, with every gesture, every word, every pat on the back,
	they have always tried to inspire us for better things and attain them. More so with this project, they
	were with us every instant, sharing our joys - when the code used to work and wiping our tears when
	machine used to hang.
	\vs
	We wish to place on record our whole hearted gratitude to \textbf{\sir} our project guide
	and \textbf{Mr. Amit Srivastava} for making available every facility that we required during the course of
	our project. Also, we are extremely thankful to you Sir, for extending your kind guidance and words
	of wisdom from your treasure trove of experience. With friendly advice and guidance at every step,
	his presence was a welcome sight throughout the project.
	
	\vs
	We are also deeply indebted to our (Head Of Department) \textbf{\hod} for her constant presence, supervision
 	and advice paid off in the culmination of this project and has helped us a great deal with this project
	with her constant words of encouragement and advice.
	\vs
	Actually, this project report is just an excuse to convey our feelings about how much we appreciate
	the amount of concern and caring that our teachers exhibit in all our pursuits ranging from anything
	as simple as the routine lab program to something as taxing as a project. Their patient listening to
	our problem is itself a major source of strength to us.
	\vs
	
	Finally, we would like to bind up by paying our heartfelt thanks and prayers to the Almighty,
	without whose willing nothing is possible in this world and all my dear friends for their
	support. 
	\pagebreak 
	
	\tableofcontents
	
	\pagebreak